{\fontfamily{ptm}\selectfont Extending the Convergence Results of Nesterov's Acceleration using the Proximal Gradient Gap}

### 2025-08-29 Notebook LaTEX/Formalized Notes/Notes on QSCNVX/main.tex
>w<, changes

\title{{\fontfamily{ptm}\selectfont Linear Convergence of Accelerated Gradient without Restart}}

@@

\begin{abstract} 
    This paper gives definitive answers to open problems in Necoara et al. \cite{necoara_linear_2019}. 
    Linear converence of Nesterov's accelerated gradient method is possible in a boarder context of functions. 
\end{abstract}

@@

\section{Introduction}
    \textbf{Notations.}
    Unless specified, our ambient space is $\RR^n$ with Euclidean norm $\Vert \cdot\Vert$.
    Let $C\subseteq \RR^n$, $\Pi_C(\cdot)$ denotes the projection onto the set $C$, i.e: the closest point in $C$ to another point in $\RR^n$. 
    We denote $\delta_C$ to be the indicator function for the set $C$. 
    For a function of $F = f + g$, and a $B\ge 0$ where $f$ is $\mathcal C^1$ differentiable, and $g$ is l.s.c, we consider the proximal gradient operator: 
    \begin{align*}
        T_B(x) &= \argmin_{z} \left\lbrace
            g(z) + f(x) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert x - z\Vert^2
        \right\rbrace
        \\
        &= \hprox_{B^{-1}g}(x - B^{-1}\nabla f(x)). 
    \end{align*}
    We also define the gradient mapping operator $\mathcal G_B(x) = B^{-1}(x - T_B(x))$.

\section{Precursors materials for our proofs of linear convergence}
    The following two definitions defines the accelerated proximal gradient algorithm. 
    % DEFINITION =======================================================================================================
    \begin{definition}[similar triangle form of accelerated proximal gradient]\;\label{def:st-apg}\\
        The definition is about $((\alpha_k)_{k \ge 0}, (q_k)_{k \ge 0}, (B_k)_{k \ge 0}, (y_k)_{k \ge 0}, (x_k)_{k \ge -1}, (v_k)_{k \ge -1})$. 
        These sequences satisfy:
        \begin{enumerate}[nosep]
            \item $x_{-1}, y_{- 1}\in \RR^n$ are arbitrary initial condition of the algorithm;
            \item $(q_k)_{k \ge 1}$ be a sequence such that $q_k \in [0, 1)$ for all $k \ge 1$;
            \item $(\alpha_k)_{k \ge 1}$ be a sequence such that $\alpha_0 \in (0, 1]$, and for all $k \ge 1$ it has $\alpha_k \in (q_k, 1)$;
            \item $(B_k)_{k \ge 0}$ has $B_k \ge 0$, it's a nonnegative sequence. 
        \end{enumerate}
        Then an algorithm satisfies the similar triangle form of Nesterov's accelerated gradient if it generates iterates $(y_k, x_k, v_k)_{k \ge 1}$ such that for all $k\ge 0$: 
        \begin{align*}
            y_k &= \left(\frac{\alpha_k - q_k}{1 - q_k}\right)v_{k - 1} 
            + \left(\frac{1 - \alpha_k}{1 - q_k}\right) x_{k - 1},
            \\
            x_k &= T_{B_k}(y_k), D_f(x_k, y_k) \le \frac{B_k}{2}\Vert x_k - y_k\Vert^2, 
            \\
            v_k &= x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
        \end{align*}
    \end{definition}
    % DEFINITION =======================================================================================================
    \begin{definition}[relaxed momentum sequence]\label{def:rlx-momentum-seq}
        The following definition is about sequences $((\alpha_k)_{k \ge 0}, (q_k)_{k \ge 0}$. 
        They satisfy:
        \begin{enumerate}[nosep]
            \item $(q_k)_{k \ge 0}$ is a sequence such that $q_k \in [0, 1)$ for all $k \ge 0$;
            \item $(\alpha_k)_{k \ge 0}$ has $\alpha_k \in (0, 1]$, and for all $k \ge 0$. 
        \end{enumerate}
    \end{definition}
    % DEFINITION =======================================================================================================
    \begin{definition}[proximal gradient gap]\label{def:pg-gap}
        Let $F = f + g$ where $f$ is $L$ Lipschitz smooth and $g$ is convex. 
        Then the proximal gradient mapping $T_B(x) = \hprox_{B^{-1}g}(x -  B^{-1}\nabla f(x))$ is a singleton, and $\dom T_B = \RR^n$. 
        Let $\mu, B$ be parameters such that $B > \mu \ge 0$. 
        We define the proximal gradient gap $\mathcal E(z, y, \mu, B)$ is the mapping: 
        \begin{align*}
            \mathcal E(z, y, \mu, B) &:= 
            F(z) - F(T_B(y)) 
            - \left\langle B(y - T_B(y)), z - y\right\rangle
            - \frac{\mu}{2}\Vert z - y\Vert^2
            - \frac{B}{2}\Vert y - T_B(y)\Vert^2. 
        \end{align*}
    \end{definition}
    \begin{remark}
        This expression is the same as the proximal gradient inequality up to a negative sign, after moving everything to one side. 
    \end{remark}

\section{Deriving the convergence rate}
    To derive the convergence rate of algorithm satisfying Definition \ref{def:st-apg}, \ref{def:rlx-momentum-seq}, we leverage Definition \ref{def:pg-gap}. 
    The first two subsections prepare for the results and the convergence results are derived by the end. 
    \par
    The following assumption is about the Proximal Gradient gap, it's required to obtain our first result. 
    % ASSUMPTION =======================================================================================================
    \begin{assumption}[generic assumptions for convergence]\label{ass:for-cnvg}
        The following assumption is about $(F, f, g, \mathcal E, \mu, L)$, it is the configuration needed to derive the convergence rate of algorithms that satisfy Definition \ref{def:st-apg}. 
        We assume that there exists $\mu \ge 0$ such that the followings are true: 
        \begin{enumerate}[nosep]
            \item Let $F = f + g$ where $f$ is $L$ Lipschitz smooth and, $g$ is closed convex and proper.
            \item $\forall y \in \RR^n, \exists B \ge 0\; \exists \bar y$ such that $\mathcal E(\bar y, y, \mu, B) \ge 0$. 
            \item For all $z, y \in \RR^n$, there exists $B > \mu$ such that $\mathcal E(z, y, \mu, B) + \frac{\mu}{2}\Vert z - y\Vert^2 \ge 0$.   
        \end{enumerate}
    \end{assumption}
    \begin{remark}
        Note that:
        \begin{enumerate}
            \item If the function $f$ is convex and smooth, $g$ is convex then, all conditions are satisfied for $\mu = 0$, and for all $\bar y \in \RR^n$. 
            \item If $\mu \ge 0$ satisfies item (ii), (iii), then it also satisfies for all $\tilde \mu$ such that $0 \le \tilde \mu \le \mu$. For the best convergence rate, the largest such $\mu$ is of our interest. 
        \end{enumerate}

@@

@@

            Let $(F, f, g,  \mathcal E, \mu, L)$ satisfies Assumption \ref{ass:for-cnvg}. 

@@

            Now, we use the above two results and it derives 

@@

                \item $(F, f, g, \mathcal E, \mu, L)$ satisfies Assumption \ref{ass:for-cnvg}. 

@@

                + \frac{B_k\alpha_k(\alpha_k - q_k)}{2}\Vert \bar x_k - v_{k - 1}\Vert^2. 

@@

@@

                    B_k(y_k - z_k), 

@@

            On the second equality above, we used $B^{-1}_k(y_k - x_k)= \mathcal G_{B_k}(y_k)$, and $B_k = \mu/q_k$.

@@

                    \frac{\alpha_k\mu}{2}\Vert y_k - \bar x_k\Vert^2

@@

                & \underset{(3)}{\le} 0. 

@@

            At (2), we used the $\mathcal E(\bar x_k, y_k, \mu, B_k)\le 0$ by choosing $\bar x_k = \bar y$ in Assumption \ref{ass:for-cnvg} (iii) to make the inequality. 
            At (3), we used Assumption \ref{ass:for-cnvg} (iv). 
            At this point, we had proved what we wanted because using the definitions of $\Xi_k, \Xi_k'$ it has:

@@

                &\le 0. 

@@

        To finally find the convergence rate, we will strengthen Assumption \ref{ass:for-cnvg}. 

@@

            Let $(F, f, g, \mathcal E, \mu, L)$ satisfies Assumption \ref{ass:for-cnvg}. 
            In addition, we strength the prior assumptions:

@@

                \item $\exists \mu > 0$ such that $\forall\; y \in \RR^n$, it has $\mathcal E \left(\Pi_{X^+}y, y, \mu, B\right) \ge 0$. 

@@

            Now, suppose an algorithm which optimizes a $F = f + g$ satisfying all pervious assumptions, and it generates iterates $(y_k, x_k, v_k)_{k\ge 0}$ that satisfies Definition \ref{def:pg-gap}. 
            In addition, we assume that the parameter sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}, (q_k)_{k \ge 0}, (B_k)_{k \ge 0}$ satisfy the following: 

@@

                \item The sequences $\alpha_k, \rho_k, q_k$ are given by Definition \ref{def:rlx-momentum-seq}. 

@@

                \item For all $k \ge 0$, $\Pi_{X^+}y_k$ is a unique. 

@@

        \begin{assumption}[Assumption for sublinear convergence rate]

@@

@@

        \begin{theorem}[linear convergence with generic sequence]\;\label{thm:cnvg-generic-seq}\\
            Let $(F, f, g, \mathcal E, \mu, L)$, and sequences $(\alpha_k)_{k \ge 0}, (\rho_k)_{k \ge 0}, (q_k)_{k \ge 0}, (B_k)_{k \ge 0}$ 

@@

            Choose $z = \bar x, y = x_{-1}$ we have from Assumption \ref{ass:for-cnvg} (iii) that

@@

            SOMETHING IS WRONG, LET US EXPLAIN.

@@

        \begin{lemma}[beta sequence bounds]\;\label{lemma:beta-seq}\\
            Let sequence $(\alpha_k)_{k \ge 0}, (\rho_{k})_{k \ge 0}, (q_k)_{k \ge 0}$ satisfies Definition \ref{def:rlx-momentum-seq}.
            Let sequences $(B_k)_{k \ge 1}$ be given by Definition \ref{def:st-apg}. 
            Define $\beta_k := \prod_{i = 1}^k(1 - \alpha_i) \max \left(\frac{B_i\rho_{i - 1}}{B_{i - 1}}, 1\right)$.
            Assume in addition that for all $k \ge 0$, $B_k = B_{k - 1} = B$. 

@@

@@

            For all $k \ge 1$ it has 

@@

                & (1 - \alpha_k)\max\left(
                    \frac{B_k\rho_{k - 1}}{B_{k - 1}}, 1

@@

                &= \max(\rho_{k - 1}(1 - \alpha_k), 1 - \alpha_k) 
                &\underset{\text{(1)}}{=} \max\left(
                    \frac{\alpha_k(\alpha_k - q)}{\alpha_{k - 1}^2}, 1 - \alpha_k

@@

                    \frac{\alpha_k^2}{\alpha_{k - 1}^2} - \frac{q}{\alpha_{k - 1}}, 1 - \alpha_k

@@

                &\underset{\text{(2)}}{\le} 
                    1 - \frac{q}{\alpha_{k - 1}}, 1 - \alpha_k

@@

            Then, observe that

@@

                1 - \frac{q}{\alpha_{k - 1}} &> 1 - \frac{q}{\sqrt{q}}

@@

            Combining the previous two results it has 

@@

                (1 - \alpha_k)\max\left(
                    \frac{B_k\rho_{k - 1}}{B_{k - 1}}, 1
                \right) \le 

@@

@@

        \end{proof}
    \subsection{Parameter free representations}

\section{Linear convergence beyond the strongly convex case}
    We will check Assumption \ref{ass:lin-cnvg} and, propose examples for it.
    In Necoara et al.'s setting, they have the following assumptions for their objective function. 
    \begin{assumption}[The settings for Necoara's et al]\;\label{ass:necoara}\\
        The assumption is about $(f, X, X^+, f^+)$ where 
            \item $X \subseteq \RR^n$ is a closed convex set. 
            \item $f: X\rightarrow \RR$ has $L$ Lipschitz continuous gradient, and it's convex. 
            \item $X^+ = \argmin_{x \in X} f(x)\neq \emptyset$, and we denote $f^+$ to be the minimum value. 
    The following definition on Quasi Strongly Convex function (Q-SCNVX) is taken from \cite[Definition 1]{necoara_linear_2019}. 
    \begin{definition}[Q-SCNVX]\label{def:Q-SCNVX}
        Let $(f, X, X^+, f^+)$ be given by Assumption \ref{ass:necoara}. 
        We define $f$ to be Quasi Strong Convex on $X$ if there exists $\kappa_f  > 0$ such that $\forall x \in \RR^n$ , with $\bar x = \Pi_{X^+}x$ it has:
            f^+ - f(x) - \langle \nabla f(x), \bar x - x\rangle - \frac{\kappa_f}{2}\Vert \bar x - x\Vert^2 
            &\ge 0. 
    \end{definition}
    \begin{proposition}[Q-SCNVX is an example of our assumptions]\label{prop:qscnvx-ass-ok}
        Let $(f, X, X^+, f^+)$ satisfies Assumption \ref{ass:necoara}.
        Let $\mathcal E$ be given by Definition \ref{def:pg-gap} with $g = \delta_X$. 
        Then for all $x \in \RR^n$, let $\bar x = \Pi_{X^+}x, x^+ = T_B(x)$, there exists $B \ge 0$, such that 
            0 &\le 
            \mathcal E(\bar x, x, B, \kappa_f)
            = 
            f(\bar x) - f(x^+) 
            - \frac{B}{2}\Vert x - x^+\Vert^2 
            - B\langle \bar x - x, x - x^+\rangle
            - \frac{\kappa_f}{2}\Vert \bar x - x\Vert^2. 
        Therefore, it satisfies Assumption \ref{ass:for-cnvg}. 
    \end{proposition}
        Let $h = z \mapsto \delta_X(z) + \langle \nabla f(x), z\rangle + \frac{B}{2}\Vert z - x\Vert^2$.
        So it has $T_B(x) = \argmin_{z\in \RR^n} h(z)$. 
        Furthermore, $h(z)$ is a $B$ strongly convex function by convexity of $X$ and, the fact that other parts are just the sum of a linear and quadratic function. 
        Denote $x^+ = T_B(x)$, since $x^+$ is a minimizer therefore it has $(\forall x \in X)\; h(z) - h(x^+) \ge \frac{B}{2}\Vert z - x^+\Vert^2$. 
        That was the quadratic growth condition of $h$. 
        Next, denote $\bar x  = \Pi_{X^+}x$, let $z = \bar x$ then the condition becomes: 
            & \frac{B}{2}\Vert \bar x - x^+\Vert^2 
            \langle \nabla f(x), \bar x\rangle + \frac{B}{2}\Vert \bar x - x\Vert^2 - 
            \langle \nabla f(x), x^+\rangle + \frac{B}{2}\Vert x^+ - x\Vert^2
            \langle \nabla f(x), \bar x - x\rangle - \langle \nabla f(x), x^+ - x\rangle
            + \frac{B}{2}\Vert \bar x - x\Vert^2 
            - \frac{B}{2}\Vert x^+ - x\Vert^2
            &= - D_f(\bar x, x) - f(x) + f(\bar x) - f(x^+) + f(x) + D_f(x^+, x)
            + \frac{B}{2}\Vert \bar x - x\Vert^2 
            - \frac{B}{2}\Vert x^+ - x\Vert^2
            - D_f(\bar x, x) + f(\bar x) - f(x^+) 
            + \frac{B}{2}\Vert \bar x - x\Vert^2 
            + D_f(x^+, x)
            - \frac{B}{2}\Vert x^+ - x\Vert^2
            &\underset{\text{(1)}}{\le} 
            - \frac{\kappa_f}{2}\Vert \bar x - x\Vert^2
            + f(\bar x) - f(x^+)
            + \frac{B}{2}\Vert \bar x - x\Vert^2 
            + 0
        At (1), we used the fact that $f$ is assumed satisfy \ref{def:Q-SCNVX} because $\bar x = \Pi_{X^+}x$, in addition the inequality $D_f(x^+, x) \le \frac{B}{2}\Vert x^+ - x\Vert^2$ is true because of Lipschitz gradient Assumption in \ref{ass:necoara} hence for all $B\ge L$, it's true for all $x$. 
        Rearranging it has 
            0 &\le
            f(\bar x) - f(x^+) 
            + \frac{B}{2}\Vert \bar x - x\Vert^2 
            - \frac{B}{2}\Vert \bar x - x^+\Vert^2
            - \frac{\kappa_f}{2}\Vert \bar x - x\Vert^2
            f(\bar x) - f(x^+) 
            - \frac{B}{2}\Vert x - x^+\Vert^2 
            - B\langle \bar x - x, x - x^+\rangle
            - \frac{\kappa_f}{2}\Vert \bar x - x\Vert^2
            &= \mathcal E(\bar x, x, B, \kappa_f). 
        The above results showed that Assumption \ref{ass:for-cnvg} (ii) has been satisfied, with $\bar y = \Pi_{X^+}y$. 
        To see (iii) in Assumption \ref{ass:for-cnvg}, observe that Assumption \ref{ass:necoara} has $f$ is convex. 

@@

>>>>

\title{{\fontfamily{ptm}\selectfont Extending the Convergence Results of Nesterov's Acceleration using the Proximal Gradient Gap}}

@@

\begin{abstract} 
    This paper gives definitive answers to open problems in Necoara et al. \cite{necoara_linear_2019}. 
    Linear convergence of Nesterov's accelerated gradient method is possible in a boarder context of functions. 
\end{abstract}

@@

\section{Introduction}
    \textbf{Notations.}
    Unless specified, our ambient space is $\RR^n$ with Euclidean norm $\Vert \cdot\Vert$.
    Let $C\subseteq \RR^n$, $\Pi_C(\cdot)$ denotes the projection onto the set $C$, i.e: the closest point in $C$ to another point in $\RR^n$. 
    We denote $\delta_C$ to be the indicator function for the set $C$. 
    For a function of $F = f + g$, and a $B\ge 0$ where $f$ is $\mathcal C^1$ differentiable, and $g$ is l.s.c, we consider the proximal gradient operator: 
    \begin{align*}
        T_B(x) &= \argmin_{z} \left\lbrace
            g(z) + f(x) + \langle \nabla f(x), z - x\rangle + \frac{B}{2}\Vert x - z\Vert^2
        \right\rbrace
        \\
        &= \hprox_{B^{-1}g}(x - B^{-1}\nabla f(x)). 
    \end{align*}
    We also define the gradient mapping operator $\mathcal G_B(x) = B^{-1}(x - T_B(x))$. 
    \par
    \textbf{Major results}.

\section{Precursors materials for our proofs of linear convergence}
    The following two definitions defines the accelerated proximal gradient algorithm. 
    % DEFINITION =======================================================================================================
    \begin{definition}[similar triangle form of accelerated proximal gradient]\;\label{def:st-apg}\\
        The definition is about $((\alpha_k)_{k \ge 0}, (q_k)_{k \ge 0}, (B_k)_{k \ge 0}, (y_k)_{k \ge 0}, (x_k)_{k \ge -1}, (v_k)_{k \ge -1})$. 
        These sequences satisfy:
        \begin{enumerate}[nosep]
            \item $x_{-1}, y_{- 1}\in \RR^n$ are arbitrary initial condition of the algorithm;
            \item $(q_k)_{k \ge 1}$ be a sequence such that $q_k \in [0, 1)$ for all $k \ge 1$;
            \item $(\alpha_k)_{k \ge 1}$ be a sequence such that $\alpha_0 \in (0, 1]$, and for all $k \ge 1$ it has $\alpha_k \in (q_k, 1)$;
            \item $(B_k)_{k \ge 0}$ has $B_k \ge 0$, it's a nonnegative sequence. 
        \end{enumerate}
        Then an algorithm satisfies the similar triangle form of Nesterov's accelerated gradient if it generates iterates $(y_k, x_k, v_k)_{k \ge 1}$ such that for all $k\ge 0$: 
        \begin{align*}
            y_k &= \left(\frac{\alpha_k - q_k}{1 - q_k}\right)v_{k - 1} 
            + \left(\frac{1 - \alpha_k}{1 - q_k}\right) x_{k - 1},
            \\
            x_k &= T_{B_k}(y_k), D_f(x_k, y_k) \le \frac{B_k}{2}\Vert x_k - y_k\Vert^2, 
            \\
            v_k &= x_{k - 1} + \alpha_k^{-1}(x_k - x_{k - 1}). 
        \end{align*}
    \end{definition}
    \begin{remark}
        If we choose $a_k = 1$ then the definition is equivalent to proximal gradient algorithm, with $v_k = x_k$ for all $k \ge 0$.

    \end{remark}
    % DEFINITION =======================================================================================================
    \begin{definition}[relaxed momentum sequence]\label{def:rlx-momentum-seq}
        The following definition is about sequences $((\alpha_k)_{k \ge 0}, (q_k)_{k \ge 0}$. 
        They satisfy:
        \begin{enumerate}[nosep]
            \item $(q_k)_{k \ge 0}$ is a sequence such that $q_k \in [0, 1)$ for all $k \ge 0$;
            \item $(\alpha_k)_{k \ge 0}$ has $\alpha_k \in (0, 1]$, and for all $k \ge 0$. 
        \end{enumerate}
    \end{definition}
    % DEFINITION =======================================================================================================
    \begin{definition}[proximal gradient gap]\label{def:pg-gap}
        Let $F = f + g$ where $f$ is $L$ Lipschitz smooth and $g$ is convex. 
        Then the proximal gradient mapping $T_B(x) = \hprox_{B^{-1}g}(x -  B^{-1}\nabla f(x))$ is a singleton, and $\dom T_B = \RR^n$. 
        Let $\mu, B$ be parameters such that $B > \mu \ge 0$. 
        We define the proximal gradient gap $\mathcal E(z, y, \mu, B)$ is the mapping: 
        \begin{align*}
            \mathcal E(z, y, \mu, B) &:= 
            F(z) - F(T_B(y)) 
            - \left\langle B(y - T_B(y)), z - y\right\rangle
            - \frac{\mu}{2}\Vert z - y\Vert^2
            - \frac{B}{2}\Vert y - T_B(y)\Vert^2. 
        \end{align*}
    \end{definition}
    \begin{remark}
        This expression is the same as the proximal gradient inequality up to a negative sign, after moving everything to one side. 
    \end{remark}
    For the sum of smooth and nonsmooth objective, a lot can be said about the proximal gradient gap of the function. 
    \begin{lemma}[proximal gradient gap under convexity]\label{lemma:pg-under-cnvx}

\section{Deriving the proximal gap inequality}
    To derive the convergence rate of algorithm satisfying Definition \ref{def:st-apg}, \ref{def:rlx-momentum-seq}, we leverage Definition \ref{def:pg-gap}. 
    The first two subsections prepare for the results and the convergence results are derived by the end. 
    The following assumption is about the Proximal Gradient gap. 
    % ASSUMPTION =======================================================================================================
    \begin{assumption}[generic assumptions for proximal gradient gap inequality]\;\label{ass:pggap-dscnt}\\
        The following assumption is about $(F, f, g, \mathcal E, \mu, L)$, it is the configuration needed to derive the convergence rate of algorithms that satisfy Definition \ref{def:st-apg}. 
        We assume that there exists $\mu \ge 0$ such that the followings are true: 
            \item\label{ass:pggap-dscnt-itm1} Let $F = f + g$ where $f$ is $L$ Lipschitz smooth and, $g$ is closed convex and proper.
            \item\label{ass:pggap-dscnt-itm2} $\forall y \in \RR^n, \exists B \ge 0\; \exists \bar y$ such that $\mathcal E(\bar y, y, \mu, B) \ge 0$. 
            % \item For all $z, y \in \RR^n$, there exists $B > \mu$ such that $\mathcal E(z, y, \mu, B) + \frac{\mu}{2}\Vert z - y\Vert^2 \ge 0$.   
    \begin{remark}
        Note that:
            \item If the function $f$ is convex and smooth, $g$ is convex then, all conditions are satisfied for $\mu = 0$, and for all $\bar y \in \RR^n$. 
            \item If $\mu \ge 0$ satisfies item (ii), (iii), then it also satisfies for all $\tilde \mu$ such that $0 \le \tilde \mu \le \mu$. For the best convergence rate, the largest such $\mu$ is of our interest. 

@@

    Using the above assumption, in this section, we can build up to Lemma \ref{lemma:cnvg-prep-part3}. 
    The lemma is crucially important and it gives us the an inequality on what happen between iterates $x_{k}, v_{k}$ and $v_{k - 1}, x_{k - 1}$ generated by algorithm satisfying Definition \ref{def:st-apg}. 

@@

            Let $(F, f, g,  \mathcal E, \mu, L)$ satisfies Assumption \ref{ass:pggap-dscnt}. 

@@

            Now, we use the above two results and, it derives 

@@

                \item $(F, f, g, \mathcal E, \mu, L)$ satisfies Assumption \ref{ass:pggap-dscnt}. 

@@

                + \frac{B_k\alpha_k(\alpha_k - q_k)}{2}\Vert \bar x_k - v_{k - 1}\Vert^2
                    -(1 - \alpha_k)\left(

@@

                F(x_{k - 1}) - F(T_{B_k}(y_k))

@@

                    B_k(y_k - T_{B_k}(y_k)), 

@@

            On the second equality above, we used $B_k(y_k - x_k)= \mathcal G_{B_k}(y_k)$, and $B_k = \mu/q_k$.

@@

                    + \frac{\alpha_k\mu}{2}\Vert y_k - \bar x_k\Vert^2

@@

@@

            At (2), we used the $\mathcal E(\bar x_k, y_k, \mu, B_k)\le 0$ by choosing $\bar x_k = \bar y$ in Assumption \ref{ass:pggap-dscnt}\ref{ass:pggap-dscnt-itm2}  to make the inequality. 
            Now, recall the definitions of $\Xi_k, \Xi_k'$ which means we proved the following: 

@@

                &\le -(1 - \alpha_k)\left(

@@

        To finally find the convergence rate, we will strengthen Assumption \ref{ass:pggap-dscnt}. 

@@

            Let $(F, f, g, \mathcal E, \mu, L)$ satisfies Assumption \ref{ass:pggap-dscnt}. 
            In addition, we strengthened the prior assumptions:

@@

                \item Strenghening Assumption \ref{ass:pggap-dscnt}\ref{ass:pggap-dscnt-itm2}, assume $\exists \mu > 0$ such that $\forall y \in \RR^n$, it has $\mathcal E \left(\Pi_{X^+}y, y, \mu, B\right) \ge 0$. 
                \item For all $y, z \in \RR^n$, it satisfies that $\mathcal E(z, y, \mu, B) + \mu/2 \Vert z - y\Vert^2 \ge 0$. 

@@

            Now, suppose an algorithm which optimizes a $F = f + g$ satisfying all previous assumptions, and it generates iterates $(y_k, x_k, v_k)_{k\ge 0}$ that satisfies Definition \ref{def:pg-gap}. 
            In addition, we assume that the parameter sequences $(\alpha_k)_{k \ge 0},(q_k)_{k \ge 0}, (B_k)_{k \ge 0}$ satisfy the following: 

@@

                \item The sequences $\alpha_k, q_k$ are given by Definition \ref{def:rlx-momentum-seq}. 

@@

                \item For all $k \ge 0$, $\Pi_{X^+}y_k$ is unique. 

@@

        \begin{assumption}[forever sublinear convergence rate in the convex case]\;\label{ass:forever-cnvx-cnvg}\\
            Let $(F, f, g, \mathcal E, \mu, L)$ satisfies Assumption \ref{ass:pggap-dscnt}. 
            In addition, we strengthened the prior assumptions:
                \item The function $f$ is convex. Hence assumption Assumtion \ref{ass:pggap-dscnt} \ref{ass:pggap-dscnt-itm2} satisfied for all $\bar y$, $\mu = 0$. 
            Now, suppose an algorithm which optimizes a $F = f + g$ satisfying all previous assumptions, and it generates iterates $(y_k, x_k, v_k)_{k\ge 0}$ that satisfies Definition \ref{def:pg-gap}. 
            In addition, we assume that the parameter sequences $(\alpha_k)_{k \ge 0},(q_k)_{k \ge 0}, (B_k)_{k \ge 0}$ satisfy the following: 
                \item The sequence $B_k \ge B_{k - 1}$, it's a non-decreasing sequence. 
                \item $\alpha_k \ge \alpha_{k - 1}$, it's a non-increasing sequence. 

@@

        \begin{assumption}[optimal convergence rate in the convex case]

        \subsection{convergence results based on these assumptions}

@@

            \begin{theorem}[convergence with generic sequence]\;\label{thm:cnvg-generic-seq}\\
                Let $(F, f, g, \mathcal E, \mu, L)$, and sequences $(\alpha_k)_{k \ge 0}, (q_k)_{k \ge 0}, (B_k)_{k \ge 0}$ 

@@

                Choose $z = \bar x, y = x_{-1}$ we have from Assumption \ref{ass:pggap-dscnt} (iii) that

@@

                SOMETHING HAS LIMITATIONS, LET US EXPLAIN.

@@

            \begin{lemma}[beta sequence linear bound]\;\label{lemma:beta-seq}\\
                Let sequences $(\alpha_k)_{k \ge 0}, (q_k)_{k \ge 0}, (B_k)_{k \ ge 0}$ satisfy Assumption \ref{ass:lin-cnvg}. 
                Define 
                \beta_k := 
                Assume in addition $\forall k \ge 0$, $\exists B : B_k = B_{k - 1} = B$ hence there exists $q$ such that $(\forall k \ge 0)\; q_k = q$. 

@@

                By the assumption that $q \in (0, 1)$ hence we had a linear convergence rate in each of the above scenarios. 

@@

                Using mononicity of sequence $\alpha_k$, it has $\alpha_i / \alpha_{i - 1} \le 1$ hence for all $i \ge 1$ it has 

@@

                    & \max\left(
                        \frac{\alpha_i(\alpha_i - q)}{\alpha_{i - 1}^2}

@@

                        1 - \alpha_i, \frac{\alpha_i - q}{\alpha_{i - 1}}

@@

                    &\le \max\left(
                        1 - \alpha_i, 1 - \frac{q}{\alpha_{i - 1}}

@@

@@

                Then, observe that when $\alpha_i \ge \sqrt{q}$ it has: 

@@

                    1 - \frac{q}{\alpha_{i - 1}} &> 1 - \frac{q}{\sqrt{q}}

@@

                Hence

@@

                        \frac{\alpha_i(\alpha_i - q)}{\alpha_{i - 1}^2}
                    \right)\le 

@@

                The result now follows by the definition of $\beta_k$. 

@@

                The proof is obvious by setting both $q_i, \alpha_i$ to be a constant. 

@@

\section{Examples for our assumptions}
    We will check Assumption \ref{ass:lin-cnvg} and, propose examples for it.
    \subsection{quasi strongly convex function}
        In Necoara et al.'s setting, they have the following assumptions for their objective function. 
        \begin{assumption}[The settings for Necoara's et al]\;\label{ass:necoara}\\
            The assumption is about $(f, X, X^+, f^+)$ where 
            \begin{enumerate}[nosep]
                \item $X \subseteq \RR^n$ is a closed convex set. 
                \item $f: X\rightarrow \RR$ has $L$ Lipschitz continuous gradient, and it's convex. 
                \item $X^+ = \argmin_{x \in X} f(x)\neq \emptyset$, and we denote $f^+$ to be the minimum value. 
            \end{enumerate}
        \end{assumption}
        The following definition on Quasi Strongly Convex function (Q-SCNVX) is taken from \cite[Definition 1]{necoara_linear_2019}. 
        \begin{definition}[Q-SCNVX]\label{def:Q-SCNVX}
            Let $(f, X, X^+, f^+)$ be given by Assumption \ref{ass:necoara}. 
            We define $f$ to be Quasi Strong Convex on $X$ if there exists $\kappa_f  > 0$ such that $\forall x \in \RR^n$ , with $\bar x = \Pi_{X^+}x$ it has:
            \begin{align*}
                f^+ - f(x) - \langle \nabla f(x), \bar x - x\rangle - \frac{\kappa_f}{2}\Vert \bar x - x\Vert^2 
                &\ge 0. 
            \end{align*}
        \end{definition}
